Topological Equivariant Artist Model

### 2021-03-09 slides/main.tex
commo
math section

@@

\begin{frame}{Image $\vmark(xpos, yposcolor)$}
    \begin{figure}[H]
        \includegraphics[width=1\textwidth]{figures/math/image.png}
    \end{figure}
    \begin{align*}
        R &= R(\vindex(\alpha, \beta))\\
        G &= G(\vindex(\alpha, \beta))\\
        B &= B(\vindex(\alpha, \beta))
    \end{align*}
\end{frame}

\section{References}
\begin{frame}[allowframebreaks]{References}
%\printbibliography
\end{frame}
\appendix 
\begin{frame}{Rendering: Define a Pixel}
    \begin{columns}
        \column{0.5\textwidth}
        Given a pixel
        \begin{equation}
        p=\left[y_{top}, y_{bottom}, x_{right}, x_{left}\right]
        \end{equation}
        the inverse map of the bounding box 
        \begin{equation}
        \gbase_{p} ={\gsection_{xy}}^{-1}(p)
        \end{equation}
        is a region $\gbase_p \subset \gbase$ such that 
        \begin{align}
            \scriptstyle r_p &= \scriptstyle \iint\limits_{S_p} \rho_r(s)ds^{2}\\
            \scriptstyle g_p &= \scriptstyle \iint\limits_{S_p} \rho_g(s)ds^{2}\\
            \scriptstyle  b_p &= \scriptstyle \iint\limits_{S_p} \rho_b(s)ds^{2}
        \end{align}
        yields the color of the pixel. 
        \column{0.5\textwidth}
        \begin{figure}[H]
            \includegraphics[width=\textwidth]{figures/math/render.png}
        \end{figure}
    \end{columns}
\end{frame}

>>>>

\begin{frame}{Sheafs}
    Restriction maps of a sheaf describe how local $\iota^*\dsection$ can be glued into larger sections \cite{ghristElementaryAppliedTopology2014,ghristHomologicalAlgebraData2018}.

    \begin{equation}
        \label{eq:sheaf}
        \begin{tikzcd}[ampersand replacement=\&]
            \iota^*\dtotal \arrow[d, "\pi"'] \arrow[r, "\iota^*", hook]             \& \dtotal \arrow[d, "\pi"']                  \\
            U \arrow[r, "\iota", hook] \arrow[u, "\iota^{*}\dsection"', bend right] \& \dbase \arrow[u, "\dsection"', bend right]
        \end{tikzcd}
    \end{equation}
    The inclusion map $\iota: U \rightarrow \dbase$ pulls \dtotal\ over $U$ such that the pulled back $\iota^*\dsection$ only contains records over $U \subset \dbase$.
\end{frame}

@@

\begin{frame}{Image $\vmark(xpos, ypos, color)$}
    \begin{figure}[H]
        \includegraphics[width=1\textwidth]{figures/math/image.png}
    \end{figure}
    \begin{align*}
        R &= R(\vindex(\alpha, \beta))\\
        G &= G(\vindex(\alpha, \beta))\\
        B &= B(\vindex(\alpha, \beta))
    \end{align*}
\end{frame}

\begin{frame}{Assembly Function Factory}
\begin{figure}[H]
    \includegraphics[width=1\textwidth]{figures/math/q_hat.png}
\end{figure}
\begin{equation}
\label{eq:qhat_q_s}
\vmarkd(\vsection(\dbasepoint))(\gbasepoint) \coloneqq \vmark((\vsectionpull)(\gbasepoint))
\end{equation} 
such \gbasepoint\ can be factored out when $\vpreimg = \gbasepoint$
\end{frame}

\begin{frame}{Composition of artists}
    Given the family of artists $(\dtotal_i: i\in I)$ on the same image
    \begin{equation}
        + \coloneqq \underset{i\in I}{\sqcup} \dtotal_{i}
    \end{equation}
    the + operator defines a simple composition of artists.

    When artists share a base space 
    \begin{equation}
        \dbase_2 \hookrightarrow \dbase_1
    \end{equation}
    a composition operator can be defined such that the the artists can be considered to be acting on different components of the same section. 
\end{frame}
\begin{frame}{Equivalance class of artists}
    An approximation of the equivalence class of artists $\vartist^{\prime}$
    \begin{equation}
    \vartist \in \vartist^{\prime}: \vartist_{1} \equiv \vartist_{2}
    \end{equation}
    roughly treats two artists as equivalent if they 
    \begin{itemize}
        \item act on the same visual bundle \vtotal
        \item have the same assembly function \vmarkd 
        \item have the same continuity map \vindex 
    \end{itemize}
\end{frame}

\section{Prototype}

\section{References}
\begin{frame}[allowframebreaks]{References}
\printbibliography
\end{frame}
\appendix 
\begin{frame}{Rendering: Define a Pixel}
    \begin{columns}
        \column{0.5\textwidth}
        Given a pixel
        \begin{equation}
        p=\left[y_{top}, y_{bottom}, x_{right}, x_{left}\right]
        \end{equation}
        the inverse map of the bounding box 
        \begin{equation}
        \gbase_{p} ={\gsection_{xy}}^{-1}(p)
        \end{equation}
        is a region $\gbase_p \subset \gbase$ such that 
        \begin{align}
            \scriptstyle r_p &= \scriptstyle \iint\limits_{S_p} \rho_r(s)ds^{2}\\
            \scriptstyle g_p &= \scriptstyle \iint\limits_{S_p} \rho_g(s)ds^{2}\\
            \scriptstyle  b_p &= \scriptstyle \iint\limits_{S_p} \rho_b(s)ds^{2}
        \end{align}
        yields the color of the pixel. 
        \column{0.5\textwidth}
        \begin{figure}[H]
            \includegraphics[width=\textwidth]{figures/math/render.png}
        \end{figure}
    \end{columns}
\end{frame}
